plots with prolactin

### 2019-12-02 analysis/16_PRL.Rmd
now with icons on manip images

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Prolactin (ng/mL)")

@@

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression")
```

>>>>

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Prolactin (ng/mL)")  +
  mytheme() +
  ylim(c(-15,80)) +
  annotation_custom(control, ymin = -20, ymax = 0, xmin = -7.5) +
  annotation_custom(bldg, ymin = -20, ymax = 0, xmin = -5.5) +
  annotation_custom(lay, ymin = -20, ymax = 0, xmin = -3.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = -1.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 0.5) +
  annotation_custom(inc, ymin = -20, ymax = 0, xmin = 2.5) +
  annotation_custom(hatch, ymin = -20, ymax = 0, xmin = 4.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 6.5) +
  annotation_custom(nestling, ymin = -20, ymax = 0, xmin = 8.5)

@@

ggplot(meanPRL, aes(treatment, m)) +
   geom_image(aes(image=music), size=.12)  +
  labs(x = "parental care stages", y = "Pituitary PRL expression") +
  mytheme() +
  ylim(c(15,22)) +
  annotation_custom(control, ymin = 15, ymax = 16.5, xmin = -7.5) +
  annotation_custom(bldg, ymin = 15, ymax = 16.5, xmin = -5.5) +
  annotation_custom(lay, ymin = 15, ymax = 16.5, xmin = -3.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = -1.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 0.5) +
  annotation_custom(inc, ymin = 15, ymax = 16.5, xmin = 2.5) +
  annotation_custom(hatch, ymin = 15, ymax = 16.5, xmin = 4.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 6.5) +
  annotation_custom(nestling, ymin = 15, ymax = 16.5, xmin = 8.5) 
```
